Development of a Python Package for Matching Observational Data

### 2022-05-05 paper/main.tex
updated thesis cover page
fixed typo: subset *on* features -> subset *of* features

\title{Development of a Python Package for Matching Observational Data}
\subtitle{Advisors: Jingshu Wang, Sanjay Krishnan}
\author{Jack Potrykus}
\date{\today}

@@

% Insert some text making clear that this is an MS thesis
\begin{center}{\large \bfseries Master’s Paper for the University of Chicago Department of Statistics}\end{center}

@@

@@

% Insert a spot for the advisor's signature
\vfill{\null}
Approved by: \hrulefill~Date: \hrulefill

\newpage{}
\tableofcontents{}
\newpage{}

@@

\paragraph{Almost Exact Matching.} Some of the most modern methods are DAME \parencite{liu_interpretable_2019} and FLAME \cite{wang_flame_2021}, which incorporate machine-learning generated weight vectors indicating the relative importance of features to extend exact matching into the field of \emph{almost exact matching}. These two algorithms are unified by their tendency to sometimes ``drop'' uninformative features from the matching process, in order to ensure that the most important features are matched on, and potentially increase the number of potential matches. The chief difference can be summarized as follows: DAME choosing a subset of features to match on by minimizing predictive error, whereas FLAME maximizes a match quality statistic that the researcher can tune via a hyperparameter; this statistic is a function of predictive error and a \emph{balance factor}, which represents the relative size of the strata of observations matched on this subset on features \parencite{gupta_dame-flame_2021}.

>>>>

\title{Development of a Python Package for Matching Observational Data}
\subtitle{{\Large Advisors: Jingshu Wang, Sanjay Krishnan}}
\author{Jack Potrykus}
\date{\today}

@@

% Insert some text making clear that this is an MS thesis
\begin{center}{\large \bfseries Master’s Paper for the University of Chicago Department of Statistics}\end{center}
\vspace{5cm}

@@

% Insert a spot for the advisor's signature
\vfill{\null}
{\Large 
  Approved by:~\hrulefill\vspace{0.5cm}\\%
  Date:~\hrulefill%
}
\newpage{}

@@

\tableofcontents{}
\newpage{}

@@

\paragraph{Almost Exact Matching.} Some of the most modern methods are DAME \parencite{liu_interpretable_2019} and FLAME \cite{wang_flame_2021}, which incorporate machine-learning generated weight vectors indicating the relative importance of features to extend exact matching into the field of \emph{almost exact matching}. These two algorithms are unified by their tendency to sometimes ``drop'' uninformative features from the matching process, in order to ensure that the most important features are matched on, and potentially increase the number of potential matches. The chief difference can be summarized as follows: DAME choosing a subset of features to match on by minimizing predictive error, whereas FLAME maximizes a match quality statistic that the researcher can tune via a hyperparameter; this statistic is a function of predictive error and a \emph{balance factor}, which represents the relative size of the strata of observations matched on this subset of features \parencite{gupta_dame-flame_2021}.
